---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: portrait
 
header-includes:
 
- \usepackage{booktabs}
- \usepackage{colortbl}
- \usepackage{subfig}
- \usepackage{floatrow}
- \usepackage{sectsty}
- \usepackage{titlesec}
- \usepackage{fontspec}
- \usepackage{float}
- \graphicspath{{/Users/aaronstaehely/Documents/CCU Analytics/Logos}}
- \newfontfamily\CoastalFont[Path=/Users/aaronstaehely/Library/Fonts/City Bold/]{City Bold.ttf}
- \newenvironment{Coastaltablefont}{\CoastalFont}{}
- \newfontfamily\NewFont[Path=/System/Library/Fonts/]{Avenir.ttc}
- \newenvironment{ctable2}{\Newfont}{}
- \newgeometry{left=1.5cm, right=1.5cm, top=0.5cm, bottom=0.1cm}
---
```{r setup, include=FALSE}
#
library(webshot)
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(flextable)
library(pandoc)
library(ggplot2)
library(cowplot)
library(plotly)
library(gridExtra)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```
\begin{center}
\CoastalFont\textbf{\LARGE `r params$catcher` - Post Game Report}
\end{center}

\vspace{-1cm}
\hspace{-6cm}
\includegraphics[width = 2cm, height = 1cm]{CCUlogo}
\hspace{14.5cm}
\vspace{-0.4cm}
\includegraphics[width = 2cm, height = 1cm]{SBClogo}
\vspace{-5mm}
\begin{center}
\CoastalFont\textbf{\Large Receiving}
\end{center}

```{r +/-, echo = FALSE, warning = FALSE }
kable(game_summary_table, table.envir = 'NewFont', format = "latex",  linesep = "") %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
      column_spec(1,border_left = TRUE) %>%
      column_spec(3, bold = T, border_left = T, color = 'white',
                  background = ifelse('Game +/-' > 0 & 'Game +/-' < 3, '#93EA8E',
                                      ifelse('Game +/-' >=3,'#339a1d',
                                             ifelse('Game +/-' < 0 & 'Game +/-' > -3, '#eaa48e', '#ba1c0f')))) %>%
      row_spec(row = 0, color = "white", background = "#006F71") %>%
      column_spec(ncol(game_summary_table), border_right = TRUE)
```
\vspace{-5mm}
\centering
```{r Today Arrange, echo = FALSE, warning = FALSE, fig.width=7.5, fig.height=3, position='center'}
grid.arrange(StolenStrikes, LostStrikes, ncol = 2)
```

```{r log, echo=FALSE, warning=FALSE }

kable(pitch_log, table.envir = 'NewFont', format = "latex",  linesep = "") %>%
      row_spec(seq(2, nrow(pitch_log), by = 2), background = "#f2f2f2") %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
      column_spec(1,border_left = TRUE) %>%
   column_spec(col=7, bold = T, border_left = T, color = 'white',background = ifelse(pitch_log$Actual == 'BALL', '#339a1d', '#ba1c0f')) %>%
      row_spec(row = 0, color = "white", background = "#006F71") %>%
      column_spec(ncol(pitch_log), border_right = TRUE)

```
\vspace{-0.5cm}
\begin{center}
\CoastalFont\textbf{\Large Throwing Report}
\end{center} 



\centering
```{r throwplot, echo=FALSE, warning=FALSE }
ThrowPlot
```

\centering
```{r tables, echo=FALSE, warning=FALSE, fig.width=2,fig.height=2}
kable(Throwlog, table.envir = 'NewFont', format = "latex",  linesep = "") %>%
      row_spec(seq(2, nrow(Throwlog), by = 2), background = "#f2f2f2") %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
      column_spec(1,border_left = TRUE) %>%
      row_spec(row = 0, color = "white", background = "#006F71") %>%
      column_spec(ncol(Throwlog), border_right = TRUE)
```








